Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-10-05 ms.tex
plugging in -> inserting, edits up to eq. 14 from Shane

Consider a sphere of radius $R$ and uniform density, with line-center optical depth $\tau_0$. We aim to find the intensity within the sphere as a function of radius and photon frequency. Photons of frequency $\nu$ near line center frequency $\nu_0$ are considered. The Doppler width will be written $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light. The photon frequency in Doppler units will be written $x = (\nu-\nu_0)/\Delta$. For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$. $n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $\mathcal{H}(x,a)$ is the Voigt function, $k = n_{\rm sc} (\pi e^2/m_e c) f$, and the Voigt line profile is $\phi = \mathcal{H}(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$. The line center optical depth is then $\tau_0 = (k/\sqrt{\pi}\Delta)R$.

Starting with the full transfer equation, Eq. \ref{eq:finaleqn}, with no photon destruction and a photon emission term given by Eq. \ref{eq:jem}, the steady-state transfer equation is
\be
\nabla^2 J + \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J}{\partial \sigma^2} & = & 
- \frac{ \sqrt{6} kL}{4\pi \Delta^2} \delta^3(\vec{x} - \vec{x}_s) \delta (\sigma - \sigma_{\rm s}).
\label{eq:rt_no_destr}
\ee
where $\sigma$ comes from a change of variables in photon frequency (Eq. \ref{eq:change_of_variables}) and $\sigma_s$ is the photon frequency of the source. The boundary condition is that there is no incoming intensity at the surface, which can be written
\citep{1986rpa..book.....R}
\be
J & = & \sqrt{3} H
\label{eq:bc}
\ee
at $r=R$.

@@

\be
H_{\rm d} & = & - \frac{1}{3k\phi} \frac{\partial J_d}{\partial r}
=  \left( \frac{1}{3k\phi} \right) 
\left( \frac{ \sqrt{6}k^3L }{ 8\pi^3 \Delta^4} \right)
\left( \frac{k r/\Delta}{ \left[ (kr/\Delta)^2 + (\sigma-\sigma_{\rm s})^2 \right]^2 } \right).
\label{eq:Hd}
\ee
This solution is useful as a simple analytic formula. However, it is not a good approximation to the true solution, as it is too large at $r=R$ by a factor of $J_{\rm d}(R,\sigma)/ H_{\rm d}(R,\sigma) \sim a\tau_0/x^2 \sim (a\tau_0)^{1/3} \gg 1$ and does not adhere to the correct boundary condition. This solution is included in Fig. \ref{fig:sol_mc_residual_0} for illustration, but will not be discussed further.

A better approximation to the true solution has been derived by \citet{2006ApJ...649...14D}, who generalized the closed-form solution in slab geometry found in \citet{1990ApJ...350..216N}. They found a solution which satisfies a $J=0$ boundary condition at $r=R$. Again, we generalize their solution to allow emission at frequency $\sigma_{\rm s}$ away from line center. The result can be written as a sum over spatial modes,
\be \label{eq:J0_sum}
J_0 = \frac{\sqrt{6}L}{16\pi \Delta} \frac{1}{R^2}\sum_{n=1}^{\infty}n\frac{\sin{\kappa_n r}}{\kappa_n r}\exp{\left(\frac{\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)},
\ee
and
\be \label{eq:H0_sum}
H_0 = - \frac{1}{3k\phi} \frac{\partial J_0}{\partial r} = -\frac{1}{3k\phi}\frac{\sqrt{6}L}{16\pi\Delta} \frac{1}{R^2}\sum_{n=1}^{\infty}n\left(\frac{\cos{\kappa_n r}}{r} - \frac{\sin{\kappa_n r}}{\kappa_n r^2}\right)\exp{\left(\frac{\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)},
\ee
which can be summed to give the closed form expressions
\be
J_0 & = & \frac{\sqrt{6}L}{32\pi^2 \Delta}
\frac{1}{Rr}
\left( 
\frac{ \sin(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] - \cos(\pi r/R)}
\right)
\label{eq:J0}
\ee
and
\be
H_0 & = &\frac{1}{3k\phi}
\frac{\sqrt{6}L}{32\pi^2 \Delta}
\frac{1}{Rr^2}
\left( 
\frac{ \sin(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] - \cos(\pi r/R)}
\right. \nonumber \\ & & \left. - \left( \frac{\pi r}{R} \right)
\frac{ \cos(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] - \cos(\pi r/R)}
+ \left( \frac{\pi r}{R} \right)
\frac{ \sin^2(\pi r/R) }{ \left[ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] - \cos(\pi r/R) \right]^2 }
\right).
\label{eq:H0}
\ee
Again $J_0 \gg H_0$, except near the $r=R$, where it goes to zero. The flux at $r=R$ can be written
\be
\nonumber
H_0(R, \sigma) & = & - \frac{1}{3k\phi}
\frac{\sqrt{6}L}{16\pi \Delta}
\frac{1}{R^3}
\sum_{n=1}^{\infty} 
n (-1)^n \exp{\left(\frac{\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)}\\
& = &  \frac{1}{3k\phi}
\frac{\sqrt{6}L}{32\pi \Delta}
\frac{1}{R^3}
\left( 
\frac{ 1 }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] +1 }
\right).
\label{eq:H0surf}
\ee
Eq. \ref{eq:H0surf} will be shown to be a much better approximation to the solution than Eq. \ref{eq:Hd}. It is still valid near the delta function at $r=0$, but is also a much better approximation at $r=R$. $J_0$ decreases exponentially rather than as a power-law in frequency as for $J_d$, giving a much smaller flux on the line wings as compared to the divergent solution.

@@

A different solution method is attempted here, namely, a continuous Fourier expansion in the frequency variable $\sigma$. The solution of this problem is split into two pieces: $J_0$ which includes the delta function source and satisfies $J=0$ at $r=R$, and $\rm J_{bc}$ which allows the boundary condition $J=\sqrt{3}H$ to be satisfied. The total solution is
\be
J(r,\sigma) & = & J_0(r,\sigma) + J_{\rm bc}(r,\sigma)
\ee
and
\be \label{eq:totalflux}
H(r,\sigma) & = & H_0(r,\sigma) + H_{\rm bc}(r,\sigma).
\ee
Here, $J_0$ and $H_0$ are the solutions of the homogeneous equation, given in Equations \ref{eq:J0} and \ref{eq:H0}. The additional term $J_{\rm bc}$ must then be a solution of the homogeneous equation
\be \label{eq:diffeq}
\frac{\partial^2J_{\rm bc}}{\partial r^2} + \frac{2}{r} \frac{\partial J_{\rm bc}}{\partial r}
+ \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J_{\rm bc}}{\partial \sigma^2} &= & 0
\ee
with no delta function source term, and it must allow the boundary conditions to be satisfied at the surface. Since $J_0(R,
\sigma)=0$, the surface boundary condition becomes
\be
J_{\rm bc}(R,\sigma) - \sqrt{3} H_{\rm bc}(R,\sigma) & = 
\sqrt{3} H_0(R,\sigma).
\label{eq:bc2}
\ee
Plugging in a frequency dependence $J_{\rm bc} \propto e^{is\sigma}$, for ``wavenumber" $s$, gives the equation for modified spherical Bessel functions of the first kind, $i_0(z)=\sinh(z)/z$. The solution can then be represented as
\be
J_{\rm bc}(r,\sigma) & = & 
\int_{-\infty}^\infty \frac{ds}{2\pi} e^{is\sigma} A(s) 
\frac{i_0(krs/\Delta)}{i_0(kRs/\Delta)},
\label{eq:Jbc}
\ee
where $A(s)$ is the Fourier amplitude. Plugging Eq. \ref{eq:Jbc} into Eq. \ref{eq:bc2} leads to the following equation for the Fourier amplitudes,
\be
\int_{-\infty}^\infty \frac{ds}{2\pi} e^{is\sigma} A(s)
\left[ 1 + \left( \frac{s}{\sqrt{3} \Delta \phi} \right) \left( \frac{i_0^\prime(kRs/\Delta)}{i_0(kRs/\Delta)} \right) \right]
& = & \sqrt{3} H_0(R,\sigma)
\label{eq:bc3}
\ee
where $H_0(R,\sigma)$ is given by Eq. \ref{eq:H0surf}. Discretization of Eq. \ref{eq:bc3} for frequency variables $\sigma_i$ and wavenumbers $s_j$
leads to a set of coupled linear equations for the $A(s_j)$. We use equally-spaced points $\Delta \sigma = 2\sigma_{\rm max}/(N-1)$ and $\Delta s = 2\pi/(N\Delta \sigma)$, where $N$ is the number of points for each grid. The result is a linear system to solve for the $A(s)$. The maximum frequency is set as $\sigma_{\rm max} = {\rm constant} \times \tau_0$, for a large enough constant that  the end of the frequency grid is at such small intensities that it does not affect the solution except close to the boundaries. The number of points was increased until the solution was well-resolved near line center, and only became inaccurate near the boundaries. Given the Fourier amplitudes, $J_{\rm bc}$ is computed using Eq. \ref{eq:Jbc}, and the flux is given by
\be
H_{\rm bc}(r,\sigma) & = & \left( \frac{-1}{3k\phi} \right)
\frac{\partial J_{\rm bc}(r,\sigma)}{\partial r}
= \left( \frac{-1}{3k\phi} \right)
\int_{-\infty}^\infty \frac{ds}{2\pi} e^{is\sigma} A(s) 
\left( \frac{ks}{\Delta} \right) 
\left( \frac{i_0^\prime(krs/\Delta)}{i_0(kRs/\Delta)} \right).
\label{eq:Hbc}
\ee
The Bessel functions are finite at the center and rise steeply toward the surface when $kRs/\Delta \gg 1$.

@@

The source is changed to the form
\be
j_{\rm em} & = & \frac{E}{4\pi} \delta^3(\vec{x} - \vec{x}_s) \delta(\nu-\nu_{\rm s})\delta (t) ,
\label{eq:jem2}
\ee
which is a standard expression for emissivity in CGS units where $E$ is the energy emitted in the impulse at time $t=0$. 
The resulting equation for $J(r,\sigma,t)$ is
\be
-3 \frac{k\phi}{c} \frac{\partial J}{\partial t} + \nabla^2 J + \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J}{\partial \sigma^2}
& = & - \frac{\sqrt{6} kE}{4\pi \Delta^2} \delta^3(\vec{x}) \delta (\sigma - \sigma_s ) \delta (t).
\label{eq:diffusion_eqn}
\ee
We employ an expansion in terms of spherical Bessel functions in $r$ and transform the time dependence into an imaginary frequency variable $\omega$. The expansion for $J(r, \sigma, t)$ is
\be
\label{eq:jrsigmat_expansion}
J(r, \sigma, t) = -\sum_{n=1}^{\infty} \int \frac{d\omega}{2\pi} e^{-i\omega t} j_0\left(\kappa_n r\right) J(n, \sigma, \omega),
\ee
with
\be \label{eq:jnsigmaomega}
J(n, \sigma, \omega) = \frac{2\kappa_n^2}{R} \int_0^R dr\ r^2 j_0(\kappa_n r) \int_0^\infty dt\ e^{i\omega t} J(r, \sigma, t).
\ee
Eq. \ref{eq:jrsigmat_expansion} is the standard specific mean intensity $dE/dA dt d\nu$. Though $J(r, \sigma, t)$ is written as a function of the photon frequency variable $\sigma$, it should be integrated over $d\nu$ to preserve its normalization. Eq. \ref{eq:jnsigmaomega} is in the same units, but with an additional unit of $t$ in the numerator as a result of the expansion. Plugging in Eq. \ref{eq:jnsigmaomega} for the eigenfunctions in Eq. \ref{eq:diffusion_eqn} and evaluating the integrals, we obtain
\be \label{eq:diffusion_plugged_in}
 \left( \frac{3k\phi}{c}i\omega  -   \kappa_n^2 \right) J(n,\sigma,\omega)  &+& \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2J(n,\sigma,\omega)}{\partial\sigma^2} = -\frac{2\kappa_n^2}{R} \frac{\sqrt{6}}{4\pi} \frac{kE}{\Delta^2} \frac{1}{4\pi} \delta(\sigma - \sigma_s).
\ee
This cannot be solved analytically, so we turn now to a semi-analytic scheme to solve this equation for $J$. We start with a treatment of the boundary conditions. At $\sigma=\sigma_s$ continuity must be enforced,
\be \label{eq:matching_condition_1}
J_+ = J_-,
\ee
and the discontinuity in $dJ/d\sigma$  must be
\be \label{eq:matching_condition_2}
\frac{\partial J_+}{\partial \sigma} - \frac{\partial J_-}{\partial \sigma} & = & 
- \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3}.
\ee
At large values of $\sigma$ the line profile is small such that Eq. \ref{eq:diffusion_plugged_in} becomes
\be \label{eq:diffusion_at_large_sigma}
\frac{\partial^2J}{\partial\sigma^2} = \frac{\Delta^2\kappa_n^2}{k^2} J,
\ee
which has solutions 
\be
J(n, \sigma, \omega)\ {\sim}\ e^{\pm \Delta \kappa_n \sigma / k}.
\ee
We then have
\be \label{eq:single_j_derivative}
\frac{\partial J}{\partial \sigma} = \mp \frac{\Delta\kappa_n}{k} J,
\ee
where a negative sign is taken for large $+\sigma$ and a positive sign is taken for large $-\sigma$. Two numerical integrations are performed inward from large $\pm \sigma$ to $\sigma_s$, isolating the solution that increases exponentially toward the line center. Initial values for integration are obtained by setting $J=1$ in Eq. \ref{eq:single_j_derivative}. This gives $J$ and $J'$ on either side of $\sigma_s$, where a prime indicates the derivative $\partial/\partial \sigma$. By enforcing the matching conditions, Eqs. \ref{eq:matching_condition_1} and \ref{eq:matching_condition_2}, the eigenfunctions $J(n, \sigma, \omega)$ are obtained for all photon frequencies $\sigma$. Since the eigenfunctions are linear in the starting conditions, only two integrations with different starting values are necessary.

>>>>

Consider a sphere of radius $R$ and uniform density, with line-center optical depth $\tau_0$. We aim to find the intensity within the sphere as a function of radius and photon frequency. Photons of frequency $\nu$ near the line center frequency $\nu_0$ are considered. The Doppler width is $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light. The photon frequency in Doppler units is $x = (\nu-\nu_0)/\Delta$. For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$. $n_{\rm sc}$ is the number density of scatterers, $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, $\mathcal{H}(x,a)$ is the Voigt function, $k = n_{\rm sc} \pi e^2 f/(m_e c)$, and the Voigt line profile is $\phi = \mathcal{H}(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$. The line center optical depth is then $\tau_0 = kR/(\sqrt{\pi}\Delta)$.

Starting with the full transfer equation, Eq. \ref{eq:finaleqn}, with no photon destruction and a photon emission term given by Eq. \ref{eq:jem}, the steady-state transfer equation is
\be
\nabla^2 J + \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J}{\partial \sigma^2} & = & 
- \frac{ \sqrt{6} kL}{4\pi \Delta^2} \delta^3(\vec{x} - \vec{x}_s) \delta (\sigma - \sigma_{\rm s}).
\label{eq:rt_no_destr}
\ee
where $J$ is the mean intensity, $\sigma$ represents a change of variables in photon frequency (Eq. \ref{eq:change_of_variables}) and $\sigma_s$ is is the photon frequency of the source. $\sigma_s$ is interchangeable with $x_s$ and $\nu_s$ in Doppler units or Hz, respectively. The boundary condition that there is no incoming intensity at the surface \citep{1986rpa..book.....R} can be written as
\be
J & = & \sqrt{3} H
\label{eq:bc}
\ee
at $r=R$.

@@

\be
H_{\rm d} & = & - \frac{1}{3k\phi} \frac{\partial J_d}{\partial r}
=  \left( \frac{1}{3k\phi} \right) 
\left( \frac{ \sqrt{6}k^3L }{ 8\pi^3 \Delta^4} \right)
\left( \frac{k r/\Delta}{ \left[ (kr/\Delta)^2 + (\sigma-\sigma_{\rm s})^2 \right]^2 } \right).
\label{eq:Hd}
\ee
This solution is useful as a simple analytic formula. However, it is not a good approximation to the true solution, as it is too large at $r=R$ by a factor of $J_{\rm d}(R,\sigma)/ H_{\rm d}(R,\sigma) \sim a\tau_0/x^2 \sim (a\tau_0)^{1/3} \gg 1$ and does not adhere to the correct boundary condition. This solution is included in Fig. \ref{fig:sol_mc_residual_0} for illustration.

A better approximation to the true solution has been derived by \citet{2006ApJ...649...14D}, who generalized the closed-form solution in slab geometry found in \citet{1990ApJ...350..216N}. They found a solution which satisfies a $J=0$ boundary condition at $r=R$. Again, we generalize their solution to allow emission at frequency $\sigma_{\rm s}$ away from line center. The result can be written as a sum over spatial modes,
\be \label{eq:J0_sum}
J_0 = \frac{\sqrt{6}L}{16\pi \Delta} \frac{1}{R^2}\sum_{n=1}^{\infty}n\frac{\sin{\kappa_n r}}{\kappa_n r}\exp{\left(\frac{\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)},
\ee
and
\be \label{eq:H0_sum}
H_0 = - \frac{1}{3k\phi} \frac{\partial J_0}{\partial r} = -\frac{1}{3k\phi}\frac{\sqrt{6}L}{16\pi\Delta} \frac{1}{R^2}\sum_{n=1}^{\infty}n\left(\frac{\cos{\kappa_n r}}{r} - \frac{\sin{\kappa_n r}}{\kappa_n r^2}\right)\exp{\left(\frac{\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)},
\ee
which can be summed to give the closed form expressions
\be
J_0 & = & \frac{\sqrt{6}L}{32\pi^2 \Delta}
\frac{1}{Rr}
\left( 
\frac{ \sin(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] - \cos(\pi r/R)}
\right)
\label{eq:J0}
\ee
and
\be
H_0 & = &\frac{1}{3k\phi}
\frac{\sqrt{6}L}{32\pi^2 \Delta}
\frac{1}{Rr^2}
\left( 
\frac{ \sin(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] - \cos(\pi r/R)}
\right. \nonumber \\ & & \left. - \left( \frac{\pi r}{R} \right)
\frac{ \cos(\pi r/R) }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] - \cos(\pi r/R)}
+ \left( \frac{\pi r}{R} \right)
\frac{ \sin^2(\pi r/R) }{ \left[ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] - \cos(\pi r/R) \right]^2 }
\right).
\label{eq:H0}
\ee
Again $J_0 \gg H_0$, except near the $r=R$, where it goes to zero. The flux at $r=R$ can be written
\be
\nonumber
H_0(R, \sigma) & = & - \frac{1}{3k\phi}
\frac{\sqrt{6}L}{16\pi \Delta}
\frac{1}{R^3}
\sum_{n=1}^{\infty} 
n (-1)^n \exp{\left(\frac{\kappa_n \Delta}{k}|\sigma - \sigma_s|\right)}\\
& = &  \frac{1}{3k\phi}
\frac{\sqrt{6}L}{32\pi \Delta}
\frac{1}{R^3}
\left( 
\frac{ 1 }{ \cosh \left[ \frac{\pi \Delta}{k R} (\sigma - \sigma_{\rm s}) \right] +1 }
\right).
\label{eq:H0surf}
\ee
Eq. \ref{eq:H0surf} will be shown to be a better approximation to the solution than Eq. \ref{eq:Hd}. It is still valid near the delta function at $r=0$, but is also a better approximation at $r=R$. $J_0$ decreases exponentially rather than as a power-law in frequency as it does for $J_d$, giving a much smaller flux on the line wings as compared to the divergent solution.

@@

A different solution method is attempted here, namely, a continuous Fourier expansion in the frequency variable $\sigma$. The solution of this problem is split into two pieces: $J_0$ which includes the delta function source and satisfies $J=0$ at $r=R$, and $\rm J_{bc}$ which allows the boundary condition $J=\sqrt{3}H$ to be satisfied. The total solution is
\be
J(r,\sigma) & = & J_0(r,\sigma) + J_{\rm bc}(r,\sigma)
\ee
and
\be \label{eq:totalflux}
H(r,\sigma) & = & H_0(r,\sigma) + H_{\rm bc}(r,\sigma).
\ee
Here, $J_0$ and $H_0$ are given in Equations \ref{eq:J0} and \ref{eq:H0}. The additional term $J_{\rm bc}$ must then be a solution of the homogeneous equation
\be \label{eq:diffeq}
\frac{\partial^2J_{\rm bc}}{\partial r^2} + \frac{2}{r} \frac{\partial J_{\rm bc}}{\partial r}
+ \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J_{\rm bc}}{\partial \sigma^2} &= & 0
\ee
with no delta function source term, and it must allow the boundary conditions to be satisfied at the surface. Since $J_0(R,
\sigma)=0$, the surface boundary condition becomes
\be
J_{\rm bc}(R,\sigma) - \sqrt{3} H_{\rm bc}(R,\sigma) & = 
\sqrt{3} H_0(R,\sigma).
\label{eq:bc2}
\ee
Inserting a frequency dependence $J_{\rm bc} \propto e^{is\sigma}$, for ``wavenumber" $s$, gives the equation for modified spherical Bessel functions of the first kind, $i_0(z)=\sinh(z)/z$. The solution can then be represented as
\be
J_{\rm bc}(r,\sigma) & = & 
\int_{-\infty}^\infty \frac{ds}{2\pi} e^{is\sigma} A(s) 
\frac{i_0(krs/\Delta)}{i_0(kRs/\Delta)},
\label{eq:Jbc}
\ee
where $A(s)$ is the Fourier amplitude. Inserting Eq. \ref{eq:Jbc} into Eq. \ref{eq:bc2} leads to the following equation for the Fourier amplitudes,
\be
\int_{-\infty}^\infty \frac{ds}{2\pi} e^{is\sigma} A(s)
\left[ 1 + \left( \frac{s}{\sqrt{3} \Delta \phi} \right) \left( \frac{i_0^\prime(kRs/\Delta)}{i_0(kRs/\Delta)} \right) \right]
& = & \sqrt{3} H_0(R,\sigma)
\label{eq:bc3}
\ee
where $H_0(R,\sigma)$ is given by Eq. \ref{eq:H0surf}. Discretization of Eq. \ref{eq:bc3} for frequency variables $\sigma_i$ and wavenumbers $s_j$
leads to a set of coupled linear equations for the $A(s_j)$. We use equally-spaced points $\Delta \sigma = 2\sigma_{\rm max}/(N-1)$ and $\Delta s = 2\pi/(N\Delta \sigma)$, where $N$ is the number of points for each grid. The result is a linear system to solve for the $A(s)$. The maximum frequency is set as $\sigma_{\rm max} = {\rm constant} \times \tau_0$, for a large enough constant that  the end of the frequency grid is at such small intensities that it does not affect the solution except close to the boundaries. The number of points was increased until the solution was well-resolved near line center, and only became inaccurate near the boundaries. Given the Fourier amplitudes, $J_{\rm bc}$ is computed using Eq. \ref{eq:Jbc}, and the flux is given by
\be
H_{\rm bc}(r,\sigma) & = & \left( \frac{-1}{3k\phi} \right)
\frac{\partial J_{\rm bc}(r,\sigma)}{\partial r}
= \left( \frac{-1}{3k\phi} \right)
\int_{-\infty}^\infty \frac{ds}{2\pi} e^{is\sigma} A(s) 
\left( \frac{ks}{\Delta} \right) 
\left( \frac{i_0^\prime(krs/\Delta)}{i_0(kRs/\Delta)} \right).
\label{eq:Hbc}
\ee
The Bessel functions are finite at the center and rise steeply toward the surface when $kRs/\Delta \gg 1$.

@@

The source is changed to the form
\be
j_{\rm em} & = & \frac{E}{4\pi} \delta^3(\vec{x} - \vec{x}_s) \delta(\nu-\nu_{\rm s})\delta (t) ,
\label{eq:jem2}
\ee
which is a standard expression for emissivity in CGS units where $E$ is the energy emitted in the impulse at time $t=0$. 
The resulting equation for $J(r,\sigma,t)$ is
\be
-3 \frac{k\phi}{c} \frac{\partial J}{\partial t} + \nabla^2 J + \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J}{\partial \sigma^2}
& = & - \frac{\sqrt{6} kE}{4\pi \Delta^2} \delta^3(\vec{x}) \delta (\sigma - \sigma_s ) \delta (t).
\label{eq:diffusion_eqn}
\ee
We employ an expansion in terms of spherical Bessel functions in $r$ and transform the time dependence into an imaginary frequency variable $\omega$. The expansion for $J(r, \sigma, t)$ is
\be
\label{eq:jrsigmat_expansion}
J(r, \sigma, t) = -\sum_{n=1}^{\infty} \int \frac{d\omega}{2\pi} e^{-i\omega t} j_0\left(\kappa_n r\right) J(n, \sigma, \omega),
\ee
with
\be \label{eq:jnsigmaomega}
J(n, \sigma, \omega) = \frac{2\kappa_n^2}{R} \int_0^R dr\ r^2 j_0(\kappa_n r) \int_0^\infty dt\ e^{i\omega t} J(r, \sigma, t).
\ee
Eq. \ref{eq:jrsigmat_expansion} is the standard specific mean intensity $dE/dA dt d\nu$. Though $J(r, \sigma, t)$ is written as a function of the photon frequency variable $\sigma$, it should be integrated over $d\nu$ to preserve its normalization. Eq. \ref{eq:jnsigmaomega} is in the same units, but with an additional unit of $t$ in the numerator as a result of the expansion. Inserting Eq. \ref{eq:jnsigmaomega} for the eigenfunctions in Eq. \ref{eq:diffusion_eqn} and evaluating the integrals, we obtain
\be \label{eq:diffusion_plugged_in}
 \left( \frac{3k\phi}{c}i\omega  -   \kappa_n^2 \right) J(n,\sigma,\omega)  &+& \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2J(n,\sigma,\omega)}{\partial\sigma^2} = -\frac{2\kappa_n^2}{R} \frac{\sqrt{6}}{4\pi} \frac{kE}{\Delta^2} \frac{1}{4\pi} \delta(\sigma - \sigma_s).
\ee
This cannot be solved analytically, so we turn now to a semi-analytic scheme to solve this equation for $J$. We start with a treatment of the boundary conditions. At $\sigma=\sigma_s$ continuity must be enforced,
\be \label{eq:matching_condition_1}
J_+ = J_-,
\ee
and the discontinuity in $dJ/d\sigma$  must be
\be \label{eq:matching_condition_2}
\frac{\partial J_+}{\partial \sigma} - \frac{\partial J_-}{\partial \sigma} & = & 
- \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3}.
\ee
At large values of $\sigma$ the line profile is small such that Eq. \ref{eq:diffusion_plugged_in} becomes
\be \label{eq:diffusion_at_large_sigma}
\frac{\partial^2J}{\partial\sigma^2} = \frac{\Delta^2\kappa_n^2}{k^2} J,
\ee
which has solutions 
\be
J(n, \sigma, \omega)\ {\sim}\ e^{\pm \Delta \kappa_n \sigma / k}.
\ee
We then have
\be \label{eq:single_j_derivative}
\frac{\partial J}{\partial \sigma} = \mp \frac{\Delta\kappa_n}{k} J,
\ee
where a negative sign is taken for large $+\sigma$ and a positive sign is taken for large $-\sigma$. Two numerical integrations are performed inward from large $\pm \sigma$ to $\sigma_s$, isolating the solution that increases exponentially toward the line center. Initial values for integration are obtained by setting $J=1$ in Eq. \ref{eq:single_j_derivative}. This gives $J$ and $J'$ on either side of $\sigma_s$, where a prime indicates the derivative $\partial/\partial \sigma$. By enforcing the matching conditions, Eqs. \ref{eq:matching_condition_1} and \ref{eq:matching_condition_2}, the eigenfunctions $J(n, \sigma, \omega)$ are obtained for all photon frequencies $\sigma$. Since the eigenfunctions are linear in the starting conditions, only two integrations with different starting values are necessary.
